Geometric variational problems

### 2020-11-08 NSF2020/Description/background.tex
added my name to title

\noindent
{\bf {Collaborative Research: Mathematical modeling and coarse-grained simulations of self-assembly of amphiphilic Janus particles in a solvent}}\\
{\it Rolf Ryham (lead PI, Fordham University)}\\
{\it Shidong Jiang (co-PI, NJIT) and Yuan-Nan Young (PI, NJIT)}
\section{Background}
\label{sec:background}
\subsection{Hydrophobic Forces}
\label{sec:hydrophobicforce}

>>>>

\noindent
{\bf {Collaborative Research: Mathematical modeling and coarse-grained simulations of self-assembly of amphiphilic Janus particles in a solvent}}\\
{\it Rolf Ryham (lead PI, Fordham University)}\\
{\it Bryan Quaife (PI, FSU) and Yuan-Nan Young (PI, NJIT)}
\section{Background}
\label{sec:background}
\subsection{Hydrophobic Forces}
\label{sec:hydrophobicforce}
